HGIS Pendleton Carbonates

### 2021-07-04 R/HGIS_pendleton_all.Rmd
Add notebook looking at all haiti carbonates.

---
title: "HGIS 2021-05-28 Carbonates"
author: "Brett Longworth"
date: "6/5/2021"
output: html_document
---

@@

Data reduction and analysis for carbonate samples run on May 28, 2021. Includes C-1, C-2, and test shell carbonates from Simon Pendleton.

```{r}

#Raw AMS data results file path
file <- here("data/USAMS052621R.txt")

# Date samples run (needed to separate other experiments with this wheel/targets)
date <- as.Date("2021-05-28")

# Positions of normalizing standards
standards <- c(5, 8, 13, 17)

# Positions of blanks for blank correction
blanks <- c(6, 9, 11)
```

@@

## raw results

```{r}
df <- process_hgis_results(file, date, standards)
#write_csv(df, here("data_analysed/HGIS_2021-05-28_raw.csv"))
#write.xlsx(df, here("data_analysed/HGIS_2021-05-28_raw.xlsx"))
```

>>>>

---
title: "HGIS Pendleton Carbonates"
author: "Brett Longworth"
date: "2021-07-05"
output: html_document
---

@@

Data analysis for Haiti core carbonates from Simon Pendleton. Data reduction is handled by `carbonate_samples.R` using the method and functions from the `hgis` package.

@@

## Load results

```{r}
df <- readRDS(here("data_analysed/carb_all.Rdata"))
#write_csv(df, here("data_analysed/HGIS_2021-05-28_raw.csv"))
#write.xlsx(df, here("data_analysed/HGIS_2021-05-28_raw.xlsx"))
```
